\documentclass[11pt,english]{article}
\usepackage{hyperref}

\input{preamble}
\begin{document}

\centerline{{\Huge \bf Philihp Busby}}
\bigskip

\contact{philihp@gmail.com}
        {philihp.com}
        {\href{https://github.com/philihp}{github.com/philihp}}
        {San Francisco, California}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{dressanomalie.com}
           {Lead Software Engineer}
           {2018-05 to 2019-10}
           
First fulltime engineer at Anomalie, building a site for managing inside sales of dress orders. Raised conversion signup rate from 10\% to 20\%.

Built machine learning algorithms turning discrete preferences toward photos into a multivariate preference vector, and running cosine similarity search to sort by ordinal affinity. Raised likelihood of bride liking the photo presented (versus control) from 25\% to 35\%.

Raised Series-A of \$13m, and Grew engineering team from one (myself) to 7 engineers.

\experience{airbnb.com}
           {Software Engineer, Full-stack web and iOS}
           {2014-06 - 2018-04}

Help center article CMS, added A/B experiment support to content and versioned translations.

Founding member of Portland engineering team.

Modified internal customer support tool to work with cohosts. Started project to separate Lantern frontend from backend, to increase performance from 6-8 second to sub-second load times.

Transitioned to mobile/iOS. Worked on Government ID and Selfie identification requirements flow.

Wrote and calibrated 4 of the 26 questions used for interviews.

\experience{sas.com}
           {Sales Engineer, Software Developer}
           {2003-07 - 2014-04}

One of three sales engineers for entire US academic sales territory. 2012, hit 129\% of sales target. 2013, hit 120\% of sales target.

Created sales demos for SAS Visual Analytics using public NCES data, added geocoding.

Presenter, 2013 Assoc. for Inst. Research, \href{http://support.sas.com/resources/papers/proceedings12/075-2012.pdf}{SAS Global Forum 2012}, \href{http://www.sesug.org/SESUG2013/abstract.html#CC-02}{SESUG 2013}.

Maintainer of SAS Global Forum registrant data warehouse.

On-call rotation for entire company's invoicing and reporting data warehouse.

Wrote internal healthcare primary care signup website in Java Struts.

Maintainer of advertising OLAP system before native OLAP cubes were a thing.

Wrote a native HTTP/1.0 client in SAS/SCL because native SAS didn't support HTTP chunking on SOAP requests when dependent system changed their EJB container.

Wrote a monitoring website that tracked a realtime sync of data with IBM MQSeries.

\end{description}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Preferred Languages}
      {Ruby, Javascript (ES7+), Elixir}

\skill{Frameworks and Libraries}
      {Redux, React, Ruby on Rails, Phoenix}

\skill{Acronyms and Trigger words}
      {SQL, OLAP, PGP, HTML, REST, \LaTeX}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{B.S. Computer Science} {North Carolina State University}
           {2002-2006}
 
Broke an all-time record in Assembly course for writing a program in as few instructions possible
Competed in regional ACM International Collegiate Programming Contest (ACM ICPC)

\end{description}

\heading{Hacks and Hobbies}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{Openskill}
           {Open source, license free competitor to Microsoft TrueSkill}
           {2020-04}

Implemented the \href{https://www.csie.ntu.edu.tw/~cjlin/papers/online_ranking/online_journal.pdf}{Weng-Lin rating system} in Javascript and Elixir. Created rating system for board game tournaments.

\experience{Tarot}
           {Game AI for Kingdomino}
           {2017-09}

Wrote a monte carlo tree search implementation to play Kingdomino, similar to
Google's AlphaGo bot. Supports multiplayer, which is unique to any MCTS
implementation I've seen.

\experience{Fields of Arle}
           {Asynchronous Boardgame Website}
           {2018}

Implemented the board game Fields of Arle in the Boardgame.io framework using Functional Programming techniques and React. Contributed improvements back to Boardgame.io framework.


\end{description}
\end{document}
