\documentclass[11pt,english]{article}
\usepackage{hyperref}
\usepackage{transparent}

\input{preamble}
\begin{document}

\centerline{{\Huge \bf Philihp Busby}}
\bigskip

\contact{philihp@gmail.com}
        {\href{https://philihp.com}{philihp.com}}
        {\href{https://github.com/philihp}{github.com/philihp}}
        {San Francisco, California}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{joinhoneycomb.com}
           {Staff Software Engineer}
           {2021-05 to 2022-12}

\{React Native, Apollo, Python, Django, Graphene, AWS, serverless, ffmpeg, postgres\}
           
Team of 7, pivoted app to targeting new parents saving photos of babies, raising DAU from 30 to 800, WAU from 180 to 1800, MAU from 400 to 3100. 

Built data warehousing and reporting stack with Postgres Preset/Superset.

Honeycomb would be acquired by Ello in 2024

\experience{dressanomalie.com}
           {Lead Software Engineer}
           {2018-05 to 2019-10}

\{Ruby on Rails, Heroku, React, React Native\}
           
First fulltime engineer, built CRM for bespoke dress orders. Iterated on frontend website pushing conversion from 10\% to 20\%.

Raised Series-A of \$13m, and grew engineering team to 7 engineers.

Built machine learning algorithms turning discrete preferences toward photos into a multivariate preference vector, and running cosine similarity search to sort by ordinal affinity.

Anomalie would be acquired by David's Bridal in 2022.

\experience{airbnb.com}
           {Software Engineer, Full-stack web and iOS}
           {2014-06 - 2018-04}

\{Ruby on Rails, Java, Javascript, React, React Native, Swift\}

I committed a net-negative number of lines of code to Github, ignoring unit tests and comments

Help center article CMS, added A/B experiment support to content and versioned translations.

Founding member of Portland engineering team.

Did iOS/mobile ID and Selfie identification requirements flow.

Wrote and calibrated 4 of the 26 questions used for interviews.

\experience{sas.com}
           {Sales Engineer, Software Developer}
           {2003-07 - 2014-04}

\{Java, Javascript, Base SAS, SAS/ETL\}

2012, hit 129\% of sales target. 2013, hit 120\% of sales target.

Created sales demos for SAS Visual Analytics using public NCES data, added geocoding.

Presenter, 2013 Assoc. for Inst. Research, \href{http://support.sas.com/resources/papers/proceedings12/075-2012.pdf}{SAS Global Forum 2012}, \href{http://www.sesug.org/SESUG2013/abstract.html#CC-02}{SESUG 2013}.

Maintainer of SAS Global Forum registrant data warehouse.

On-call rotation for entire company's invoicing and reporting data warehouse.

Wrote a native HTTP/1.0 client in SAS/SCL because native SAS didn't support HTTP chunking on SOAP requests when dependent system changed their EJB container.

\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{B.S. Computer Science} {North Carolina State University}
           {2002-2006}
 
Broke an all-time record in Assembly course for writing a program in as few instructions possible
Competed in regional ACM International Collegiate Programming Contest (ACM ICPC)

\end{description}

\heading{Hacks and Hobbies}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{Kennerspiel.com}
           {a place to play this niche board games I like}
           {2022-12}

I wanted to play the board game Ora et Labora like I used to in college with my mates, but we are all busy adults now, so I made a website where we could play it virtually and asynchronously.

\experience{Openskill}
           {an open source, license free replacement to Microsoft TrueSkill}
           {2020-04}

I wrote this in Elixir, ported it to Javascript, another guy ported it to Python, and now it's used in the game Beyond All Reason an open source RTS game on Windows and Linux.

\experience{Tarot}
           {Game AI for Kingdomino}
           {2017-09}

Wrote a game AI implementation of monte carlo tree search (used in
Google's AlphaGo), but unique to my implementation was support of multiplayer games.

\experience{Blinkydome}
           {an art installation at burning man}
           {2016, 2018, 2019, 2023, 2024}

I build this \href{https://www.instagram.com/p/B2CdlKqnNXD/}{a 32 foot diameter dome} every year with almost 8000 blinky LEDs on mapped to a 3D-shader.

\end{description}
\end{document}
